---
title: "About Me"
output: 
  html_document:
    toc: false
    toc_float: false
---
Updated: October 31, 2023
$$\\$$


### Education
```{r ,echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|       |          | 
|---------------|:--------------|
| 04/2014-03/2020       | **Hamamatsu University School of Medicine, Shizuoka, Japan** | 
||Doctor of Medicine (MD), March 2020  |
| 04/2022-03/2023      | **St. Luke’s International University Graduate School of Public Health**, Tokyo, Japan      |  
||Master of Public Health (MPH), March 2023 |
| 09/2023-present | **Columbia University Mailman School of Public Health**, New York, NY     |  
||Master of Science in Biostatistics, Expected graduation: May 2025 |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```


$$\\$$

### Work Experience
```{r ,echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|       |          | 
|---------------|:--------------|
| 04/2020-03/2022       | Full-time Resident Physician at Keio University Hospital, Tokyo, Japan | 
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

$$\\$$

### Research in Progress
Nobuhisa Morimoto, Hasan Jamil, Mohab Alakkari, Yuki Joyama, Tatsuhiko Anzai, Kunihiko Takahashi, Soichiro Iimori.   
Associations between dietary potassium intake and urinary potassium excretion.   
PROSPERO 2022 CRD42022357847 [[link]](https://www.crd.york.ac.uk/prospero/display_record.php?ID=CRD42022357847) 

$$\\$$

## Skills
**Computer**: R, Stata, Git  
**Languages**: Japanese (Native), English (Professional working proficiency), Chinese (Limited working proficiency)



