---
title: "About Me"
output: 
  html_document:
    toc: false
    toc_float: false
---
Updated: June 3rd, 2025
<br><br>


### Education
```{r ,echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|       |          | 
|---------------|:--------------|
| 04/2014-03/2020       | **Hamamatsu University School of Medicine, Shizuoka, Japan** | 
||Doctor of Medicine (MD)  |
| 04/2022-03/2023      | **St. Luke’s International University Graduate School of Public Health, Tokyo, Japan**      |  
||Master of Public Health (MPH) |
| 09/2023-05/2025 | **Columbia University Mailman School of Public Health, New York, NY**     |  
||Master of Science (MS) in Biostatistics - Public Health Data Science Track |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```


<br><br>

### Work Experience
```{r ,echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|       |          | 
|---------------|:--------------|
| 04/2020-03/2022       | **Full-time Resident Physician at Keio University Hospital, Tokyo, Japan** | 
|        | • Provide direct patient care under supervision, including history-taking, physical exams, and clinical decision-making  | 
| 05/2024-12/2025       | **Full/Part-time Content Intern at MDCalc, New York** | 
|        | • Collaborate with the editorial and medical content teams to research and develop high-quality clinical decision tools used by healthcare professionals globally  | 
| 10/2024-Present       | **Part-time Research Assistant (Biostatistics) at Tokyo Medical University Gastroenterology Dept., Tokyo, Japan** | 
|        | • Provide biostatistics consulting for physician-led research projects, including study design, sample size estimation, data analysis, and reporting  | 
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

<br><br>

### Research Experience
**Published**  
Evaluation of cesarean delivery risk by physician sex. Joyama Y, Hayasaka M, Robbins LS, Saade G, Kawakita T.
American journal of perinatology. May 19, 2025. doi:10.1055/a-2615-5055. [[link]](https://pubmed.ncbi.nlm.nih.gov/40389258/)  

Associations between dietary potassium intake and urinary potassium excretion: a protocol for systematic review and meta-analysis. Morimoto N, Jamil H, Alakkari M, Joyama Y, et al.
Syst Rev. 2024;13(1):185. doi:10.1186/s13643-024-02603-3. [[link]](https://pubmed.ncbi.nlm.nih.gov/39020425/)

**In Progress**  
Safety assessment of endoscopic papillectomy in older patients   
• Planning and performing statistical analysis using data from electronic health record  

Analysis of endoscopic techniques to prevent delayed bleeding after endoscopic papillectomy  
• Designed and conducted propensity score-matched cohort analyses to assess clinical outcomes; in process of submission  

**Academic Projects**  
Investigation of menopause as a moderator in the relationship between physical activity and cognitive aging    
• Collaborated with school faculty (Dr. Seonjoo Lee) to conduct data visualization and regression analyses, assessing the moderating role of menopausal status on cognitive benefits of physical activity


<br><br>

### Skills
**Data Analysis and Visualization**: R, SAS, Stata, Shiny, SQL, Metabase  
**Computer**: JavaScript, HTML, Git, Microsoft Office  
**Languages**: Japanese (fluent), English (proficient), Chinese (conversational)



